How has the Brazilian Amazon been constructed as a problem? Presidential speeches in transnational politics since 1985

### 2022-09-01 Draft_September_2022/Full_draft_20220901.rmd
#newfolder

---
title: How has the Brazilian Amazon been constructed as a problem? Presidential speeches in transnational politics since 1985
author:
- Livio Silva-Muller
- Henrique Sposito^[Both co-authors contributed equally to the article; names are ordered alphabetically. Livio is a PhD Candidate in Anthropology and Sociology at the Geneva Graduate Institute and affiliated to the Albert Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
date: "8 June 2022"
output:
  word_document:
    reference_docx:
  fig_caption: yes
  pdf_document: default
  html_document:
    df_print: paged
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
always_allow_html: TRUE
bibliography: references.bib
csl: chicago.csl
abstract: Presidential speeches legitimize ways of thinking about the environment transnationally, while affecting decisions at the local level.Albeit the importance of understanding the relationship between the social construction of the environment and its effects on environmental outcomes, research on presidential discourse is scarce. We lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments. Building on @hirschman1963 and @bacchi2009 conceptualization of chosen problems, we propose a framework to investigate how heads of government construct the environment in transnational political discourse. Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in all 6130 official presidential speeches since 1985. We interpret our findings in light of policies adopted and important events. First, we find national and international events drive the frequency of the Amazon as a topic in presidential speeches equally inside and outside Brazil. Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015. Constructing the Amazon as an issue of sovereignty also became more pertinent after 2010. Finally, we find that the farthest presidents are from the Amazon, the more likely they are to state the Amazon needs to be preserved. Conceptually, we argue that these are evidence of presidents maximizing contradictory political outcomes domestically and internationally.
---

@@

Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(color = "darkgreen") +
  geom_line(aes(y=mean(perc)), color="black", size=.5)+
  scale_y_continuous(labels = percent_format()) + 
  annotate("text", x = 1988.7, y = 0.34, label = "Chico Mendes", size = 3)+
  annotate("text", x = 1992, y = 0.27, label = "Earth Summit", size = 3)+
  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
  annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
  annotate("text", x = 2019, y = 0.26, label = "Red Sky afternoon \n in Sao Paulo", size=3) +
  labs(x = "", y = "",
       subtitle = "All speeches inside and outside Brazil (n=6130)",
       caption = "",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "bottom")

# location plots
Amazon_year_in <- perc_in %>%
  ggplot(., aes(x = year, y = perc))+
  geom_line(color="darkgreen")+
  geom_line(aes(y=mean(perc)), color="black", size=.5)+
  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
  scale_y_continuous(labels = percent_format())+
  labs(x = "", y = "",
       subtitle = "Speeches in Brazil (n=4344)",
       caption= " ",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "")

Amazon_year_out <- perc_out %>% 
  ggplot(., aes(x = year, y = perc))+
  geom_line(color="darkgreen")+
  geom_line(aes(y=mean(perc)), color="black", size=.5)+
  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
  scale_y_continuous(labels = percent_format())+
  labs(x = "", y = "",
       subtitle = "Speeches outside of Brazil (n=1786)",
       caption= "Black lines portray the means.",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "")

grid.arrange(Amazon_year, arrangeGrob(Amazon_year_in, Amazon_year_out, ncol=2), nrow=2, top="Speeches mentioning the Amazon since 1985")

@@

all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
  geom_jitter(alpha=.2)+
  geom_smooth(size = .5) +
  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
  scale_y_continuous(labels = percent_format()) + 
  labs(x = "Distance from the Amazon (km)",
       y = "",
       title = "Predicted share of each problem-construction as a function of distance from the Amazon",
       subtitle="Sovereignty was removed because of statistical insignificance (table 2).", 
       caption = "Curve in the plot is estimated using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
          legend.position="bottom")

@@

```{r Table 2, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}

@@

md<-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov, 
                         type = "text",
                         digits = 10, 
                         dep.var.labels = c("Conservation", "Economic Integration", "Social Development", "Sovereignty"),
                         covariate.labels = c("Distance from the Amazon (km)", "Election year", "Yearly Deforestation", "Yearly   Inflation"),
                         no.space = TRUE)

@@

model_comp <- tibble::tibble("Dependent Variable" = c("Environmental Conservation", 
"Economic Integration", "Social Development", "National Sovereignty"),
"Distance to Manaus(km)" = c("0.0001*** (0.00002)", "-0.0001** (0.00002)", "-0.0001** (0.00004)", "0.00001 (0.00002)"),
"Election Year" = c("0.288* (0.157)", "-0.022 (0.133)", "0.329* (0.171)", "-0.449* (0.269)"),
"Deforestation Year" = c("-0.032*** (0.011)", "0.041*** (0.008)", "-0.072*** (0.013)", "-0.032* (0.017)"),
"Annual Average Inflation" = c("0.0004*** (0.0001)", "-0.0002** (0.0001)", "-0.0002 (0.0002)", "0.0002 (0.0002)"),
"Constant" = c("-1.718*** (0.191)", "-1.569*** (0.160)", "-0.910*** (0.214)", "-2.301*** (0.289)"))
kbl(t(model_comp), booktabs = T,caption = "Logistic Regression Models Compared", align = "c") %>%
  kable_styling(latex_options = c("striped", "scale_down"),
                position= "center", font_size = 9, full_width = TRUE) %>%
                footnote(general = c("The regression coefficients are displayed in log odds and standard errors are displayed in parentheses.",
                "*** for p-value < 0.01, ** for p-value < 0.05, * for p-value < 0.1")) %>% 
  column_spec(1, width="3 cm", bold=TRUE, latex_valign = "m") %>%
  column_spec(2, width="2 cm", latex_valign = "m") %>%
  column_spec(3, width = "2 cm", latex_valign = "m") %>%
  column_spec(4, width = "2 cm", latex_valign = "m") %>%
  column_spec(5, width="2 cm", latex_valign = "m")
```

>>>>

---
title: How has the Brazilian Amazon been constructed as a problem? Presidential speeches in transnational politics since 1985
author:
- Livio Silva-Muller
- Henrique Sposito^[Both co-authors contributed equally to the article; names are ordered alphabetically. Livio is a PhD Candidate in Anthropology and Sociology at the Geneva Graduate Institute and affiliated to the Albert Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
date: "1 September 2022"
output:
  pdf_document: default
  fig_caption: yes
  html_document:
    df_print: paged
  word_document:
    reference_docx:
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
always_allow_html: TRUE
bibliography: references.bib
csl: chicago.csl
abstract: Presidential speeches legitimize ways of thinking about the environment transnationally, while affecting decisions at the local level.Albeit the importance of understanding the relationship between the social construction of the environment and its effects on environmental outcomes, research on presidential discourse is scarce. We lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments. Building on @hirschman1963 and @bacchi2009 conceptualization of chosen problems, we propose a framework to investigate how heads of government construct the environment in transnational political discourse. Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in all 6130 official presidential speeches since 1985. We interpret our findings in light of policies adopted and important events. First, we find national and international events drive the frequency of the Amazon as a topic in presidential speeches equally inside and outside Brazil. Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015. Constructing the Amazon as an issue of sovereignty also became more pertinent after 2010. Finally, we find that the farthest presidents are from the Amazon, the more likely they are to state the Amazon needs to be preserved. Conceptually, we argue that these are evidence of presidents maximizing contradictory political outcomes domestically and internationally.
---

@@

Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(color = "darkgreen") +
  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
  scale_y_continuous(labels = percent_format()) + 
  annotate("text", x = 1988.7, y = 0.34, label = "Chico Mendes", size = 3)+
  annotate("text", x = 1992, y = 0.27, label = "Earth Summit", size = 3)+
  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
  annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
  annotate("text", x = 2019, y = 0.26, label = "Red Sky afternoon \n in Sao Paulo", size=3) +
  labs(x = "", y = "",
       subtitle = "All speeches inside and outside Brazil (n=6130)",
       caption = "",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "bottom")

Amazon_year

# location plots
Amazon_year_in <- perc_in %>%
  ggplot(., aes(x = year, y = perc))+
  geom_line(color="darkgreen")+
  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype= "dotted")+
  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
  scale_y_continuous(labels = percent_format())+
  labs(x = "", y = "",
       subtitle = "Speeches in Brazil (n=4344)",
       caption= " ",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "")

Amazon_year_out <- perc_out %>% 
  ggplot(., aes(x = year, y = perc))+
  geom_line(color="darkgreen")+
  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype= "dotted")+
  scale_y_continuous(labels = percent_format())+
  labs(x = "", y = "",
       subtitle = "Speeches outside of Brazil (n=1786)",
       caption= "Black lines portray the means.",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "")

grid.arrange(Amazon_year_in, Amazon_year_out, ncol=2, top="Speeches mentioning the Amazon since 1985")

@@

all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
  geom_jitter(alpha=.2, size=1)+
  geom_smooth(size = .5, se=FALSE) +
  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
  scale_y_continuous(labels = percent_format()) + 
  labs(x = "Distance from the Amazon (km)",
       y = "",
       title = "Predicted share of each problem-construction as a function of distance from the Amazon",
       subtitle="Sovereignty was removed because of statistical insignificance (table 2).", 
       caption = "Curve in the plot is estimated using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
          legend.position="bottom")

@@

```{r Table 2, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

@@

md<-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov, 
                         type = 'text',
                         digits = 10, 
                         dep.var.labels = c("Conservation", "Economic Integration", "Social Development", "Sovereignty"),
                         covariate.labels = c("Distance from the Amazon (km)", "Election year", "Yearly Deforestation", "Yearly   Inflation"),
                         no.space = TRUE)

@@

model_comp <- tibble::tibble("Dependent Variable" = c("Environmental Conservation", 
"Economic Integration", "Social Development", "National Sovereignty"),
"Distance to Manaus(km)" = c("0.0001*** (0.00002)", "-0.0001** (0.00002)", "-0.0001** (0.00004)", "0.00001 (0.00002)"),
"Election Year" = c("0.288* (0.157)", "-0.022 (0.133)", "0.329* (0.171)", "-0.449* (0.269)"),
"Deforestation Year" = c("-0.032*** (0.011)", "0.041*** (0.008)", "-0.072*** (0.013)", "-0.032* (0.017)"),
"Annual Average Inflation" = c("0.0004*** (0.0001)", "-0.0002** (0.0001)", "-0.0002 (0.0002)", "0.0002 (0.0002)"),
"Constant" = c("-1.718*** (0.191)", "-1.569*** (0.160)", "-0.910*** (0.214)", "-2.301*** (0.289)"))
kbl(t(model_comp), booktabs = T,caption = "Logistic Regression Models Compared", align = "c") %>%
  kable_styling(latex_options = c("striped", "scale_down"),
                position= "center", font_size = 9, full_width = TRUE) %>%
                footnote(general = c("*** for p-value < 0.01, ** for p-value < 0.05, * for p-value < 0.1")) %>% 
  column_spec(1, width="3 cm", bold=TRUE, latex_valign = "m") %>%
  column_spec(2, width="2 cm", latex_valign = "m") %>%
  column_spec(3, width = "2 cm", latex_valign = "m") %>%
  column_spec(4, width = "2 cm", latex_valign = "m") %>%
  column_spec(5, width="2 cm", latex_valign = "m")
```
